\section{Experience}
\subsection{Academic Services}
\cventry{2014 -- 2015}{Reviewer}{Information and Software Technology}{}{}{Reviewed manuscript No. INFSOF-D-14-00238 and INFSOF-D-14-00238R1}
\cventry{2014}{Reviewer}{The 11th Working Conference on Mining Software Repositories (MSR 2014)}{}{}{Reviewed Submission \#10 and \#19}
\cventry{2013}{Student Volunteer}{The 35th International Conference on Software Engineering (ICSE 2013)}{San Francisco}{}{}
\cventry{2012}{Reviewer}{The 9th Working Conference on Mining Software Repositories (MSR 2012)}{}{}{Reviewed Submission \#46 and \#55}
\cventry{2009}{Subreviewer}{The 25th IEEE International Conference on Software Maintenance}{}{}{Reviewed Submission \#157}

\subsection{Research}
\cventry{2010 -- 2015}{Graduate Student Researcher}{University of California}{Santa Cruz, CA, USA}{}{
Projects:
\begin{itemize}
\item Worked on \textsc{CHEKOFV} project, funded by DARPA's CSFV program, that tried to build games for crowd sourced formal verification. In the first game, \textit{Xylem}, I worked as the main backend (Node.js and Express) developer and one of key developers of the game client (ActionScript 3). In the second game, \textit{Binary Fission}, I worked as the main backend (Python and Flask) developer.
\item Worked on a NASA funded project \textit{Understanding the Design Space of Mixed Initiative Robot Design Tools}, developed the prototype, \textit{Botprint} in JavaScript. It used Raphael.js to sketch the robot chassis in 2D, and Three.js to render it in 3D.
\item Worked on a NSF funded project on bug prediction. Extended the open source project \textit{CVSAnalY} to identify commits that introduce buggy code chunks.
\end{itemize}
}

\subsection{Working}
\cventry{2015--present}{Software Engineer}{Microsoft}{Redmond, WA, USA}{}{}
\cventry{2014}{SDET Intern}{Microsoft}{Redmond, WA, USA}{}{}
\cventry{2013}{Software Engineering Intern}{Google}{Mountain View, CA, USA}{}
{Developed a JavaScript fuzzer that generates random JavaScript to test Closure Compiler.}
\cventry{2008 -- 2009}{Part-time Software Engineer, Database Administrator, System Administrator}{Hoolai Social Game Ltd}{Beijing, China}{}{
	\begin{itemize}
		\item Developed several social network games using Ruby On Rails and Adobe Flex, one of which had more than 600 thousand Daily Active Users at its peak
		\item Setting up and maintaining a web infrastructure comprised of an Nginx/lighttpd server as load balancer, and several Nginx/lighttpd servers with several Phusion Passenger processes on each server to process more than 10 million HTTP requests every day
		\item Configuration and optimization of the MySQL and Memcached servers
	\end{itemize}
}                % arguments 3 to 6 are optional
\cventry{2007}{Intern}{Xiamen Shepherd Co., Ltd}{Xiamen, China}{}{Used ROR and adopted Extreme Programming practices to develop several projects, including a Agile development management system AgilePlanner and an on-line music composition website ComposeItYourself.}                % arguments 3 to 6 are optional

\subsection{Teaching}
\cventry{2011}{Teaching Assistant}{University of California}{Santa Cruz, CA, USA}{}{Courses: \textit{Machine Learning and Data Mining}, \textit{Introduction to Database Management Systems}, and \textit{Introduction to Computer Science}}



